Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring

### 2014-05-30 evaluation.tex
Fleshed out evaluation section with 200m inst data and some fake data.

\subsection{Coverage with Adjustable Overheads}
Coverage and overhead budget accuracy for source, last-minute, and min-point dropping.

%\subsection{Randomness for Multi-Run Coverage}

>>>>

\subsection{Coverage with Adjustable Overheads}

% BC sweep
\begin{figure*}
  \begin{center}
    \includegraphics[width=\linewidth]{figs/data_bc_sweep.pdf}
    \vspace{-0.4in}
    \caption{Coverage versus varying overhead budget for array bounds check.}
    \label{fig:evaluation.bc_sweep}
    \vspace{-0.2in}
  \end{center}
\end{figure*}

% UMC sweep
\begin{figure*}
  \begin{center}
    \includegraphics[width=\linewidth]{figs/data_umc_sweep.pdf}
    \vspace{-0.4in}
    \caption{Coverage versus varying overhead budget for uninitialized memory check.}
    \label{fig:evaluation.umc_sweep}
    \vspace{-0.1in}
  \end{center}
\end{figure*}

Although the overheads of DIFT are quite low after filtering, BC and UMC still
show significant overheads. In this section, we evaluate the effectiveness of
using partial monitoring to trade-off coverage for further reduced overheads.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds check as we vary the overhead budget. We measure monitoring
coverage monitoring check operations that are still performed as a percentage
of the total number of monitoring check operations. This number does not
include the number metadata update operations that are done and serves as a
better metric for the actual coverage of the security or reliability technique.
The overhead is measured as a percentage of the program without monitoring. An
unrestricted dropping policy is used here.

We see that by varying the overhead budget, the coverage achieved also varies.
Furthermore, with only a 50\% overhead budget, array bounds check still
achieves 87\% monitoring coverage on average. This overhead budget corresponds
to 26\% of the average overheads seen by BC after filtering. The high coverage
achieved with such low overheads is due to two main effects.  The first is that
monitoring can be done in parallel, providing monitoring coverage without
introducing overheads. The second effect is that, although we aggressively
filter out monitoring events, there may still exist a large number of
monitoring events that do not lead to security or reliability checks. As a
result, dropping these events can reduce overheads without a large impact on
monitoring coverage.

Figure~\ref{fig:evaluation.umc_sweep} shows the analogous graph for UMC. Again
we see that varying overhead budgets enables partial monitoring. We see that
with a 50\% overhead budget, UMC achieves 50\% monitoring coverage on average.
This overhead budget corresponds to only 15\% of the overheads seen by UMC
after filtering.

\subsection{Comparing Dropping Policies}

In this section we evaluate the trade-offs of the three dropping policies
presented in Section~\ref{sec:policies.events}: unrestricted dropping, source
dropping, and sub-flow dropping.

% BC exec time
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/data_bc_exec_time.pdf}
    \vspace{-0.2in}
    \caption{Error in meeting overhead budget for array bounds check.}
    \label{fig:evaluation.bc_exec_time}
    \vspace{-0.2in}
  \end{center}
\end{figure}

% UMC exec time
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/data_umc_exec_time.pdf}
    \vspace{-0.2in}
    \caption{Error in meeting overhead budget for uninitialized memory check.}
    \label{fig:evaluation.umc_exec_time}
    \vspace{-0.2in}
  \end{center}
\end{figure}

First, we evaluate how well the different policies are able to meet a specified
overhead budget. Figures~\ref{fig:evaluation.bc_exec_time} and
\ref{fig:evaluation.umc_exec_time} show the difference between the run-time
overheads seen and the overhead specified. These errors are averaged over all
benchmarks. A positive value means that the
overhead target was overshot while a negative value indicates that the
overheads were below the specified budget.

% BC coverage across policies
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/data_bc_coverage.pdf}
    \vspace{-0.2in}
    \caption{Coverage for array bounds check for different dropping policies.}
    \label{fig:evaluation.bc_coverage}
    \vspace{-0.2in}
  \end{center}
\end{figure}

% UMC coverage across policies
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/data_umc_coverage.pdf}
    \vspace{-0.2in}
    \caption{Coverage for uninitialized memory check for different dropping policies.}
    \label{fig:evaluation.umc_coverage}
    \vspace{-0.1in}
  \end{center}
\end{figure}

Next, we evaluate the coverage achieved by the different policies.
Figure~\ref{fig:evaluation.bc_coverage} shows the average coverage across
benchmarks for each of the three policies with varying overhead budgets.
Figure~\ref{fig:evaluation.umc_coverage} shows this data for uninitialized
memory check.
